SMT-Boosted Security Types for Low-Level MPC

### 2024-10-10 esop25/smt.tex
checkpoint

In previous work we have shown that the semantics of $\minicat$ in
$\mathbb{F}_2$ can be implemented with Datalog
\cite{skalka-near-ppdp24}, which is a form of constraint
programming. In this paper we extend this idea to arbitrary prime
fields by using a more general form of SMT constraint programming,
specifically Satisfiability Modulo Finite Fields \cite{SMFF}. As we
will show in subsequent sections, this interpretation supports
correctness guarantees, and also static type analyses for enforcing
confidentiality and integrity properties.

@@

The mapping $\toeq{\cdot}$ from programs $\prog$ to contraints
is defined in Figure \ref{fig-toeq}. The interpretion of OT is ommitted
from this figure which is general-- for $\mathbb{F}_2$ the interpretation
is:
\begin{mathpar}
  \toeq{\elab{\OT{\be_1}{\cid_1}{\be_2}{\be_3}}{\cid_2}} =
  (\toeq{\elab{\be_1}{\cid_1}} \ftimes \toeq{\elab{\be_3}{\cid_2}}) \fplus
  (\neg\toeq{\elab{\be_1}{\cid_1}} \ftimes \toeq{\elab{\be_2}{\cid_2}}) 
\end{mathpar}
In general we will assume that any preprocessing predicate is defined
via a constraint $\eqspre$, i.e., $\preproc(\store) \iff \store
\models \eqspre$ for all $\store$.  The correctness of the
SMT interpretation of programs is characterized as follows.
\begin{theorem}
  $\store$ is a model of $\eqspre \wedge \toeq{\prog}$ iff $\store \in \runs(\prog)$.
\end{theorem}

>>>>

In previous work it was shown that the semantics of $\minicat$ in
$\mathbb{F}_2$ can be implemented with Datalog
\cite{skalka-near-ppdp24}, which is a form of constraint
programming. In this paper we extend this idea to arbitrary prime
fields by using a more general form of SMT constraint programming,
specifically Satisfiability Modulo Finite Fields \cite{SMFF}. As we
will show in subsequent sections, this interpretation supports
correctness guarantees, and also static type analyses for enforcing
confidentiality and integrity properties.

@@

The mapping $\toeq{\cdot}$ from programs $\prog$ to contraints
is defined in Figure \ref{fig-toeq}. The interpretion of OT is ommitted
from this figure which is general-- for $\mathbb{F}_2$ the interpretation
is:
\begin{mathpar}
  \toeq{\elab{\OT{\be_1}{\cid_1}{\be_2}{\be_3}}{\cid_2}} =
  (\toeq{\elab{\be_1}{\cid_1}} \ftimes \toeq{\elab{\be_3}{\cid_2}}) \fplus
  (\neg\toeq{\elab{\be_1}{\cid_1}} \ftimes \toeq{\elab{\be_2}{\cid_2}}) 
\end{mathpar}
In general we will assume that any preprocessing predicate is defined
via a constraint $\eqspre$, i.e., $\preproc(\store) \iff \store
\models \eqspre$ for all $\store$.  The correctness of the
SMT interpretation of programs is characterized as follows.
\begin{theorem}
  \label{theorem-toeq}
  $\store$ is a model of $\eqspre \wedge \toeq{\prog}$ iff $\store \in \runs(\prog)$.
\end{theorem}
